Test-driven Knowledge Graph Construction

### 2023-05-11 doc/paper4.tex
Add SPARQL highlighting by @hank05-vse

%%% Colors
\definecolor{light-gray}{RGB}{245,245,245}
\definecolor{darkgreen}{RGB}{0, 153, 0}
\definecolor{iri}{RGB}{0,0,0}
\definecolor{prefix}{RGB}{0,0,195} %dark blue
\definecolor{afterPrefix}{RGB}{0,0,245}

@@

@@

\begin{lstlisting}[caption=Example competency question in SPARQL, label={lst:example-cq-sparql}]
PREFIX act:     <https://covidtesty.vse.cz/vocabulary#>
PREFIX dcterms: <http://purl.org/dc/terms/>
PREFIX ncit:    <http://purl.obolibrary.org/obo/NCIT_>
PREFIX rdf:     <http://www.w3.org/1999/02/22-rdf-syntax-ns#>
PREFIX schema:  <http://schema.org/>

>>>>

%%% Colors
\definecolor{light-gray}{RGB}{245,245,245}
\definecolor{darkgreen}{RGB}{0, 153, 0}
\definecolor{iri}{RGB}{0,0,0}
\definecolor{prefix}{RGB}{0,0,195} %dark blue
\definecolor{afterPrefix}{RGB}{0,0,245}
\definecolor{colorcomment}{RGB}{0, 153, 0}
\definecolor{mahogany}{RGB}{153,0,0}
\definecolor{darkblue}{RGB}{0,0,200}

@@

%%% SPARQL
\lstdefinelanguage{SPARQL}
{
  morecomment=[l][\color{gray}]{\#},       % comments
  morecomment=[n][\color{black}]{<http}{>}, % uris
  morestring=[b][\color{black}]{\"},  % strings
  % -------------------------- variables
  keywordsprefix=?,
  classoffset=0,
  keywordstyle=\color{darkblue},
  morekeywords={},
  % -------------------------- prefixes
  classoffset=1,
  keywordstyle=\color{orange},
  morekeywords={act,dcterms,ncit,rdf,schema},
  % -------------------------- keywords
  classoffset=2,
  keywordstyle=\color{purple},
  morekeywords={ASK,a,PREFIX}
}

@@

\begin{lstlisting}[language=SPARQL, caption=Example competency question in SPARQL, label={lst:example-cq-sparql}]
PREFIX act:     <https://covidtesty.vse.cz/vocabulary#>
PREFIX dcterms: <http://purl.org/dc/terms/>
PREFIX ncit:    <http://purl.obolibrary.org/obo/NCIT_>
PREFIX rdf:     <http://www.w3.org/1999/02/22-rdf-syntax-ns#>
PREFIX schema:  <http://schema.org/>
